Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-10-04 Paper.Rmd
2nd draft complete

-   show other works which are in line with your results,

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher. This way they are able to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments don't offer diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

-   more elab is needed here
-   you can discuss about the fluidity of search and exp attributes, tv is an experience goods in the original work

@@

-   talk about the correlation table where rating and sentiment has the expected correlations

@@

-   heterogeneous opinions, row 10,

@@

-   talk about review and reviewer related determinant, search/exp classification is too simple,

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is. Secondly, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Lastly, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature.

>>>>

@@

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher. This way consumers are able to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments don't offer diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

@@

@@

@@

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived from potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data. This increases the value of EDA as well.
